### 2016-09-06 main.tex

We have used this detector for song alignment and feedback experiments
in 5 behaving birds, and for offline analysis on a few others.  For
simplicity, and to test robustness to imperfect choice of ``syllable'', we present performance on 6 randomly chosen points in one
bird's song.  However, the results presented here are representative of
real-world performance over many birds in our lab.

@@

We define the accuracy of the network based on its classification
performance per frame. In order to avoid the apparent problem of every
non-detected non-syllable counting as a true negative, we also tried
defining accuracy on a per-song basis, such that a song without the
target syllable counted as a single true negave.  Computing the
optimal output thresholds on a per-frame rather than a per-song basis resulted in higher
thresholds and thus a slight reduction in both the false-positive and true-positive rates (reversible by increasing $C_n$), while also providing a valid
definition of false-positive rate for data streams that had not been
segmented into song-sized chunks and thus allowing easy interpretation
of false-positive rates from calls, cage noise, etc.

@@

An example of the detector's output for three of these syllables is
shown in \fig{fig:detection_raster}.  The total audio energy of each
song is shown as a single grayscale row.  By sorting according to time
of each syllable's detection, the rest of the song is shown in the
context of the timing for that moment.  This gives an intuition of the
timing variability within each song and across songs (which may be
responsible for some of our measured jitter).

@@

We allowed our training software to allocate our default of 4 hidden
units per syllable, and computed a new FFT every 1.5 ms.  Because our
timing test files are designed for our stereo playback software,
allowing only one channel for the ground-truth pulse, we trained one
detector for each syllable for the following results.  In order to
eliminate the large number of variables involved in microphone, cage,
playback and re-digitising, we evaluated the neural network's accuracy
directly on the digitised recording.  When training and runtime data
are gathered on the same hardware setup, this is the digital signal
that the detector will see---only the non-song data may be different.
%Accuracy \marginpar{Should be! Verify! And/or explain that there is a bug in the LabVIEW implementation, if there in fact is. ALSO need to present a picture of the test syllable or etc\dots} is identical across the three detectors.

\noprint{
  The means of the false positive and

  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_1$
    & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.34\% & 0.0015\%\\ 
    neg & 0.0355\% & 99.99970\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_2$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.92903\% & 0.000596\%\\ 
    neg & 0.0710\% & 99.99940\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_3$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.68062\% & 0.00194\%\\ 
    neg & 0.319\% & 99.99806\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_4$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.82257\% & 0.00239\%\\ 
    neg & 0.177\% & 99.99761\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_5$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.78708\% & 0\\ 
    neg & 0.213\% & 100\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
  \begin{tabular}{r|cc}
    $t^*_6$ & \multicolumn{2}{c}{True} \\ 
    & pos & neg \\ 
    \hline  Detected pos & 99.71611\% & 0.00552\%\\ 
    neg & 0.284\% & 99.99448\%\\ 
  \end{tabular}
  \vspace{8pt}\par\noindent
}

>>>>

We have used this detector for song alignment and feedback experiments
in 5 behaving birds, and for offline analysis on a few others.  For
simplicity, and to test robustness to imperfect choice of ``syllable'', we present performance on 6 randomly chosen points in one
bird's song.  The results presented here are representative of
real-world performance over many birds in our lab.

@@

We define the accuracy of the network based on its classification
performance per frame. In order to avoid the apparent problem of every
non-detected non-syllable counting as a true negative, we also tried
defining accuracy on a per-song basis, such that a song-length sample without the
target syllable counted as a single true negative.  Computing the
optimal output thresholds on a per-frame rather than a per-song basis resulted in higher
thresholds and thus a slight reduction in both the false-positive and true-positive rates (reversible by increasing $C_n$), while also providing a valid
definition of false-positive rate for data streams that had not been
segmented into song-sized chunks and thus allowing easy interpretation
of false-positive rates from calls, cage noise, etc.

@@

An example of the detector's output for three of these syllables is
shown in \fig{fig:detection_raster}.  The total audio energy of each
song is shown as a single grayscale row.  By sorting according to time
of each syllable's detection, the rest of the song is shown in the
context of the timing for that moment.  This gives an intuition of the
timing variability within each song and across songs (which is
responsible for a small amount of our measured jitter, but note that few of the songs are significantly timeshifted).

@@

We allowed our training software to allocate our default of 4 hidden
units per syllable, and computed a new FFT every 1.5 ms.  Because our
timing test files are designed for our stereo playback software,
allowing only one channel for the ground-truth pulse, we trained one
detector for each syllable for the following results.  In order to
eliminate the large number of variables involved in microphone, cage,
playback and re-digitising, we evaluated the neural network's accuracy
directly on the digitised recording.  When training and runtime data
are gathered on the same hardware setup, this is the digital signal
that the detector will see---only the non-song data may be different.
